\textls[-0]{\thetitle}

### 2023-03-18 metatheory-condensed.tex
Add table for four signatures The table is inlined in the text, I believe you will reformat at the end, it is just help you to copy and paste the content.
move

@@

\item We illustrate the structure of W-type signature (as a list) here. $\wsig_{\texttt{tm}}^0, \wsig_{\texttt{tm}}^1$ are (the subparts of) the signatures of constructors \{"tm\_unit"\} and \{"tm\_unit","tm\_app"\} respectively. Each item in this W-type signature, having two types, corresponds to one constructor, where the first type stores the non-recursive part of the constructor and the second type stores the ``arity'' of the  recursive part. For example, the type of $"app" : ("tm" \to "tm" \to "tm")$ $\cong (\bbone \times (\bbtwo \to "tm") \to "tm")$, corresponds to the premise of rule \ruleref{tm/wsup} (where $\wsigproj{0}{1}{\wsig_{\texttt{tm}}^1} = \bbone, \wsigproj{0}{2}{\wsig_{\texttt{tm}}^1} = \lambda \_ . \bbtwo$). This type means there is no information on non-recursive part (thus use unit type $\bbone$) and the ``arity'' of the recursive part is $\bbtwo$ and thus $\wsig_{\texttt{tm}}^1 = \WSigAdd{\wsig_{\texttt{tm}}^0}{\bbone}{\lambda \_ .\bbtwo}$.  The story is similar for $\wsig_{\texttt{tm}}^0$, where there is no recursive part at all and thus the ``arity'' is zero.\YZ{Feels like it's more straightforward to just list the encodings of the four constructors of tm in a table, assuming an encoding of the identifier type. And this paragraph should be moved to the earlier paragraph on W-types. I'll take a stab at this.}

Generally speaking, the expressiveness of W-types comes from the ``arity'', as it encodes the case when recursive structure stores as the output of a function, mirroring the strict positivity of Inductive type.
\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{\bot}$
and typed with $\El{\mathit{self}.\texttt{tm}}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, \lsti{tm} has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\mathit{self}.\texttt{tm}}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.

>>>>

\medskip

\begin{tabular}{|
>{\columncolor[HTML]{FFFFFF}}l |l|l|l|}
\hline
$\wsig_{\texttt{tm}}^{\texttt{unit}} \coloneq \WSigAdd{\WSigEmp}{\bbone}{\lambda \_ . \bbzero}$ 
& $\wsig_{\texttt{tm}}^{\texttt{var}} \coloneq \WSigAdd{\wsig_{\texttt{tm}}^{\texttt{unit}}}{"id"}{\lambda \_ . \bbzero}$
& $\wsig_{\texttt{tm}}^{\texttt{abs}} \coloneq \WSigAdd{\wsig_{\texttt{tm}}^{\texttt{var}}}{"id"}{\lambda \_ .\bbone} $ 
& $\wsig_{\texttt{tm}}^{\texttt{app}} \coloneq \WSigAdd{\wsig_{\texttt{tm}}^{\texttt{abs}}}{\bbone}{\lambda \_ .\bbtwo}$  \\ \hline
\end{tabular}

We illustrate the structure of W-type signature (as a list) here.
$\wsig_{\texttt{tm}}^0, \wsig_{\texttt{tm}}^1$ are (the subparts of) the
signatures of constructors \{"tm\_unit"\} and \{"tm\_unit","tm\_app"\}
respectively. Each item in this W-type signature, having two types, corresponds
to one constructor, where the first type stores the non-recursive part of the
constructor and the second type stores the ``arity'' of the  recursive part. For
example, the type of $"app" : ("tm" \to "tm" \to "tm")$ $\cong (\bbone \times
(\bbtwo \to "tm") \to "tm")$, corresponds to the premise of rule
\ruleref{tm/wsup} (where $\wsigproj{0}{1}{\wsig_{\texttt{tm}}^1} = \bbone,
\wsigproj{0}{2}{\wsig_{\texttt{tm}}^1} = \lambda \_ . \bbtwo$). This type means
there is no information on non-recursive part (thus use unit type $\bbone$) and
the ``arity'' of the recursive part is $\bbtwo$ and thus $\wsig_{\texttt{tm}}^1
= \WSigAdd{\wsig_{\texttt{tm}}^0}{\bbone}{\lambda \_ .\bbtwo}$.  The story is
similar for $\wsig_{\texttt{tm}}^0$, where there is no recursive part at all and
thus the ``arity'' is zero.\YZ{Feels like it's more straightforward to just list
the encodings of the four constructors of tm in a table, assuming an encoding of
the identifier type. And this paragraph should be moved to the earlier paragraph
on W-types. I'll take a stab at this.}

Generally speaking, the expressiveness of W-types comes from the ``arity'', as
it encodes the case when recursive structure stores as the output of a function,
mirroring the strict positivity of Inductive type.

\medskip

@@

\item 
The next four fields model the four constructors of~\lsti{tm}.
Constructor \lsti{tm_unit} is modeled as $\Wsup{}{\wsig_{\texttt{tm}}}{\top}{\bot}$
and typed with $\El{\mathit{self}.\texttt{tm}}$, where $\mathit{self}$ stands for
the typing context containing the first field~\lsti{tm}.
The W-type signature $\wsig_{\texttt{tm}}$ is exposed in
this typing context; that is, \lsti{tm} has type $\TyS{\wcode{\wsig_{\texttt{tm}}}}$.
So $\El{\mathit{self}.\texttt{tm}}$ and $\El{\wcode{\wsig_{\texttt{tm}}}}$ can be equated,
as required by rule \ruleref{tm/wsup}.
